Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-03-31 src/tex/ms.tex
GPT pass of Result

%\definecolor{rb4}{HTML}{27408B}
%\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
%\newcommand{\kl}[1]{\color{cyan}[KL: #1 ]}
\newcommand{\ripple}{\texttt{ripple}}
\newcommand{\python}{\texttt{python}}
\newcommand{\jax}{\texttt{jax}}
\newcommand{\zdethp}{\texttt{zdethp}}

@@

First, to judge the performance of the optimization scheme, we take $\sim530$ NR
waveforms from the SXS catalog. We choose testing waveforms with negligible
eccentricity (${e<2\times10^{-3}}$) and precession
(${\chi_{x,y}<5\times10^{-3}}$) to fit with the limitation of the model. We see
that in Fig.~\ref{fig:intrin_space}, testing waveforms have intrinsic parameters
that are within the parameter space spanned by training waveforms. Hence, we can
take these testing waveforms to compare with the original model.

We first examine the effect of joint optimization on a single waveform. In
Fig.~\ref{fig:0154}, we can see that the optimized waveform has better accuracy
than the original waveform, especially in the inspiral region, where the
amplitude has a $50\%$ decrease in error. We have chosen one of the testing
waveforms listed in \citep{khan2016frequency} for a fair comparison. 
% In general, most waveforms within the neighborhood of the training waveforms
% show improvement in mismatches.

Using a constant noise spectrum with $\mathcal{L}_{\mathrm{mean}}$, we compute
the mismatch for all testing waveforms and plot the distribution of the mismatch
in Fig. \ref{fig:q148}. We find the distribution's peak has shifted to the end
with a lower mismatch. Quantitatively, the peak has lowered by almost an
order-of-magnitude and the median of distribution has a $\sim50.0\%$ decrease.
Using $\mathcal{L}_{\mathrm{fl}}$, the mismatch distribution also has a similar
improvement. We see that the median of distribution has a $22.9\%$ decrease.
However, the distribution does not have a clear peak as Fig.~\ref{fig:q148}.
This is due to the problem mentioned in section \ref{subsec:optimization}.
Nevertheless, both distributions show improvement and the potential problem did
not affect the optimization scheme significantly.

>>>>

%\definecolor{rb4}{HTML}{27408B}
%\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
%\newcommand{\kl}[1]{\color{cyan}[KL: #1 ]}
\newcommand{\ripple}{\texttt{ripple}}
\newcommand{\python}{\texttt{python}}
\newcommand{\jax}{\texttt{jax}}
\newcommand{\zdethp}{\texttt{zdethp}}
\definecolor{rb4}{HTML}{27408B}
\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}

@@

To evaluate the effectiveness of our optimization approach, we analyze
approximately 530 NR waveforms from the SXS catalog in this study. We
specifically select waveforms with negligible eccentricity
(${e<2\times10^{-3}}$) and precession (${ \chi_{x,y}<5\times10^{-3}}$) that are
consistent with the constraints of the waveform model. As shown in
Fig.~\ref{fig:intrin_space}, the intrinsic parameters of the chosen test
waveforms fall within the parameter space defined by the training waveforms.
This suggests that these test waveforms can be used for direct comparison with
the original model.

We begin by investigating the impact of joint optimization on an individual
waveform. Fig. \ref{fig:0154} illustrates that the optimized waveform
outperforms the original waveform, particularly in the inspiral region, where
the amplitude displays a $50\%$ reduction in error. To ensure fairness, we
selected one of the testing waveforms from the catalog presented in
\citep{khan2016frequency}.
% In general, most waveforms within the neighborhood of the training waveforms
% show improvement in mismatches.

We use a constant noise spectrum, $\mathcal{L}{\mathrm{mean}}$, to evaluate the
mismatch of all testing waveforms, and present the resulting distribution in
Fig. \ref{fig:q148}. The peak of the distribution has shifted towards a lower
mismatch, with a decrease of almost one order of magnitude and a 50\% reduction
in the median. When using $\mathcal{L}{\mathrm{fl}}$, we observe a similar
improvement with a 22.9\% decrease in the median. However, the distribution lacks
a clear peak due to the problem discussed in Section \ref{subsec:optimization}.
Despite this, both distributions exhibit significant improvement, and the
optimization scheme remains unaffected.
